Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-06 manuscript.Rmd
mean travel time variability

>>>>

```{r travel_time_variance}
travel_time_sf_nontreat <- travel_time_sf %>%
	filter(march_inaug == 0) %>%
	group_by(GEOID) %>%
	summarise(mtt_mean = mean(mean_travel_time),
						mtt_var = var(mean_travel_time),
						mtt_sd = sd(mean_travel_time))
```

```{r}
travel_time_sf_nontreat %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mtt_mean)) +
	theme_map +
	scale_fill_viridis_c()

travel_time_sf_nontreat %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mtt_sd)) +
	theme_map +
	scale_fill_viridis_c()
```
